Mixed effect tweedie model in TMB

### 2019-03-16 analysis/tmb-sensor-explore/2-fit-temperature.Rmd

@@

ggplot(predictions3$data, aes(depth_scaled, residuals)) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~year)

>>>>

m_temp3_rw <- sdmTMB(d_fit,
  temperature_c ~ 0 + as.factor(year),
  time_varying =  ~ 0 + poly(depth_scaled, 3),
  include_spatial = FALSE, ar1_fields = TRUE,
  time = "year", spde = spde, family = gaussian(link = "identity"),
  silent = FALSE)

@@

predictions3_rw <- predict(m_temp3_rw)
predictions3_rw$data$residuals <- residuals(m_temp3_rw)

ggplot(predictions3_rw$data, aes(depth_scaled, residuals)) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~year)
